Implementation and Analysis of Homomorphic Facial Image Encryption and Manipulation

### 2019-01-10 paper/paper-conf.tex
New results

\subsection{Partially Homomorphic Cryptosystems}

In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

@@

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2)=(m_1+k)\bmod n & \text{ (used to add a constant)}\\
  D(E(m_1)E(m_2)\bmod n^2)=(m_1+m_2)\bmod n & \text{ (used for binary addition)}\\
  D(E(m_1)^k\bmod n^2)= km_1\bmod n & \text{ (used to multiply a plaintext constant)}
\end{align*}

@@

\paragraph{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These operations are defined as follows.
For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k)=(m_1+k)\bmod u & \text{ (used to add a constant)}\\
    D(E(m_1)E(m_2))=(m_1+m_2)\bmod u & \text{ (used for binary addition)}\\
    D(E(m_1)^k)= km_1\bmod u & \text{ (used to multiply a plaintext constant)}
\end{align*}

@@

\paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[XOR on ciphertexts]
	A bitwise exclusive or (XOR) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
	\end{align*}
	\item[AND on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise AND of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

@@

The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license. The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
\begin{itemize}
	\item Arithmetic operations: addition, subtraction, multiplication;
	\item Binary operations: AND, OR, NOT, XOR.
\end{itemize}

@@

\subsubsection{Eigenfaces}

Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.3\textwidth]{figures/secure_eigenfaces.png}
    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}.}
\end{figure}

@@

\subsection{Secure Computation with Real Numbers}
We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align*}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align*}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}
A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running under Linux.

@@

@@

\subsection{Summary}
In summary, the study consists of:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using standard test images from~\cite{gonzalez_image_nodate}.
\end{itemize}

@@

\subsection{Intensity Transformations}
The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set.

\subsubsection{Image Negation}
Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image. In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero and the SSIM being exactly equal to one.

@@

\begin{table}[!h]
    \caption{Image negation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & inf & 1.00000 & 0.128 & 0.013 & 0.041 \\
		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.084 & 0.013 & 0.024 \\
		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.031 \\
		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.109 & 0.012 & 0.048 \\
		\texttt{martin} & 0.000 & inf & 1.00000 & 0.117 & 0.015 & 0.043 \\
		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.111 & 0.012 & 0.025 \\
		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.099 & 0.012 & 0.023 \\
		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.084 & 0.012 & 0.024 \\
		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.089 & 0.012 & 0.023 \\
		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[!h]
    \caption{Image negation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & inf & 1.00000 & 0.221 & 30.217 & 0.239 \\
		\texttt{bplyce} & 0.000 & inf & 1.00000 & 0.190 & 30.919 & 0.216 \\
		\texttt{drbost} & 0.000 & inf & 1.00000 & 0.284 & 31.182 & 0.268 \\
		\texttt{ksunth} & 0.000 & inf & 1.00000 & 0.225 & 32.581 & 0.223 \\
		\texttt{martin} & 0.000 & inf & 1.00000 & 0.220 & 32.220 & 0.271 \\
		\texttt{pmives} & 0.000 & inf & 1.00000 & 0.287 & 31.224 & 0.294 \\
		\texttt{rnpwil} & 0.000 & inf & 1.00000 & 0.285 & 29.478 & 0.284 \\
		\texttt{sbains} & 0.000 & inf & 1.00000 & 0.186 & 29.784 & 0.362 \\
		\texttt{swewin} & 0.000 & inf & 1.00000 & 0.243 & 38.407 & 0.220 \\
		\texttt{yfhsie} & 0.000 & inf & 1.00000 & 0.285 & 29.488 & 0.449 \\		
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Logarithm Transformation}
\begin{table}[!h]
    \caption{Logarithm transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[!h]
    \caption{Logarithm transformation under Dasgupta--Pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Power-Law Transformation}
\begin{table}[!h]
    \caption{Power-law transformation under Paillier}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 3910.678 & 12.208 & 0.46712 & 0.099 & 14.695 & 0.024 \\
		\texttt{bplyce} & 873.064 & 18.720 & 0.84379 & 0.139 & 16.190 & 0.023 \\
		\texttt{drbost} & 1261.059 & 17.123 & 0.77229 & 0.082 & 13.866 & 0.023 \\
		\texttt{ksunth} & 653.049 & 19.981 & 0.90673 & 0.083 & 15.507 & 0.023 \\
		\texttt{martin} & 646.310 & 20.026 & 0.88157 & 0.108 & 15.727 & 0.045 \\
		\texttt{pmives} & 2047.933 & 15.018 & 0.69408 & 0.113 & 14.728 & 0.034 \\
		\texttt{rnpwil} & 806.473 & 19.065 & 0.85346 & 0.082 & 14.253 & 0.024 \\
		\texttt{sbains} & 616.419 & 20.232 & 0.92334 & 0.121 & 14.415 & 0.023 \\
		\texttt{swewin} & 8270.696 & 8.955 & 0.43185 & 0.112 & 14.362 & 0.065 \\
		\texttt{yfhsie} & 1715.478 & 15.787 & 0.73857 & 0.145 & 20.239 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}

\section{Conclusion}

\subsection{Ongoing and Future Work}

>>>>

\subsection{Partially Homomorphic Cryptosystems}
In this section, we will present two classical partially homomorphic cryptosystems which we will be testing in the study: the Paillier cryptosystem and the DGK cryptosystem. Both of these cryptosystems encrypt integer plaintexts and are additively homomorphic.

@@

The decryption function to decrypt a ciphertext $c \in \mathbb{Z}^\ast_{n^2}$ given a private key $(p,q)$ is defined as:
\begin{align*}
  D(c) = L(c^\lambda \bmod n^2) \times (L(g^\lambda \bmod n^2))^{-1} \mod n
\end{align*}

\paragraph{Homomorphic Properties of the Paillier Cryptosystem}
The Paillier cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_n$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
  D(E(m_1)g^k\bmod n^2) &=(m_1+k)\bmod n\\
  D(E(m_1)E(m_2)\bmod n^2) &=(m_1+m_2)\bmod n\\
  D(E(m_1)^k\bmod n^2) &= km_1\bmod n
\end{align*}

@@

\paragraph{Homomorphic Properties of the DGK Cryptosystem}
The DGK cryptosystem supports additive homomorphism as well as the multiplication of a plaintext scalar to an encrypted message. These homomorphic properties are used to add a plaintext scalar to a ciphertext, add two ciphertexts, and multiply a ciphertext by a plaintext scalar, respectively. They are defined as follows.

For all $m_1,m_2 \in \mathbb{Z}_u$ and $k\in \mathbb{N}$, the following homomorphic properties hold.
\begin{align*}
    D(E(m_1)g^k) &=(m_1+k)\bmod u\\
    D(E(m_1)E(m_2)) &=(m_1+m_2)\bmod u\\
    D(E(m_1)^k) &= km_1\bmod u
\end{align*}

@@

\paragraph{Homomorphic Properties of the Dasgupta--Pal Cryptosystem}
It has been shown \cite{dasgupta_design_2016} that the following properties hold for all integer messages $m_1, m_2 \in \mathbb{Z}_n$ in the Dasgupta--Pal cryptosystem. These properties arise since each coefficient in a ciphertext polynomial is essentially an independently encrypted bit of the original message.
\begin{description}
	\item[\textsc{xor} on ciphertexts]
	A bitwise exclusive or (\textsc{xor}) operation on integer messages can be achieved by adding the coefficients pairwise between two ciphertexts.
	\begin{align*}
		D(E(m_1)+E(m_2)) = m_1 \textsc{ xor } m_2
	\end{align*}
	\item[\textsc{and} on ciphertexts]
	Similarly, pair-wise multiplication corresponds to bitwise \textsc{and} of integer messages.
	\begin{align*}
		D(E(a) \otimes E(b)) = a \textsc{ and } b = ab \bmod 2
	\end{align*}
	where $\otimes$ denotes pairwise multiplication,
	\begin{align*}
		\sum_{i=1}^n{a_ix^i} \otimes \sum_{i=1}^n{b_ix^i} = \sum_{i=1}^n{a_ib_ix^i}.
	\end{align*}
\end{description}

@@

The \textit{HElib} library has been adapted to Python using the Pyfhel library \cite{pyfhel_2018} maintained by Ibarrondo, Laurent (SAP) and Onen (EURECOM), and licensed under the GNU GPL v3 license. The Pyfhel library is a Python API for the \textit{HElib} library, which supports the following operations on vectors/scalars of integers or binary ciphertexts:
\begin{itemize}
	\item Arithmetic operations: addition, subtraction, multiplication;
	\item Binary operations: \textsc{and}, \textsc{or}, \textsc{not}, \textsc{xor}.
\end{itemize}

@@

\subsubsection{Eigenfaces}
Proposed by Matthew Turk and Alex Pentland, the eigenfaces method uses principal component analysis (PCA) in order to express an input image as a linear combination of eigenfaces \cite{turk_eigenfaces_1991}. An \textit{eigenface} is a principal component, or more simply an eigenvector that represents a certain variation between the face images which are taken from the initial training set. The number of resulting eigenfaces is equal to the number of face images in the training set.

@@

\begin{figure}[!h]
    \centering
    \includegraphics[width=0.4\textwidth]{figures/secure_eigenfaces.png}
    \caption{Diagram of the privacy-preserving facial recognition process \cite{hutchison_privacy-preserving_2009}}
\end{figure}

@@

\subsection{Secure Computation with Real Numbers}
We will briefly discuss a protocol to enable cryptosystems built for integer inputs to handle real number inputs.
The following protocol was also used by \textit{CryptoImg} for image processing \cite{ziad_cryptoimg:_2016}.
This is also used for our own implementation of the Dasgupta--Pal cryptosystem in order to handle real numbers.

@@

Similar to the logarithm transformation, we must provide an approximation for $x^\gamma$.
We have derived an infinite series in Appendix \ref{sec:logapproximation}.
\begin{align}
	x^\gamma &= \sum_{n=0}^{\infty}{\frac{(\gamma\log{x})^n}{n!}}
\end{align}
Partial sums of the above infinite series can be calculated based on the closed form approximation for the logarithm in Equation \ref{eq:scaledquadraturech3}. For the implementation of the power-law transformation, a partial sum consisting of the first five terms of the infinite series were used.

\subsection{Assessment of Homomorphic Encryption Schemes}
A laptop computer with a 2.5 GHz Intel Core i7 quad-core processor and 8 GB of RAM is used to perform the computations, and processing time was tracked using built-in timing functions. The processing time for all cases were recorded. All of the tests are done using Python 3.7.1 running on Linux.

@@

For each cryptosystem, three image operations are tested:
\begin{enumerate}
	\item Image negation
	\item Logarithm transformation, with $c = 30$
	\item Power-law transformation, with $c = 1$ and $\gamma = 0.4$
\end{enumerate}

@@

\subsection{Summary}
In summary, the study consists of:
\begin{itemize}
	\item Creating a wrapper library that acts as a unified interface which implements the Paillier, DGK, Dasgupta--Pal, and BGV homomorphic cryptosystems.
	\item An implementation of image processing operations (intensity transformations, facial recognition) under the above cryptosystems.
	\item Conducting tests for image quality, processing time, using images from the \texttt{faces94} dataset.
\end{itemize}

@@

\subsection{Intensity Transformations}

\begin{table*}
	\caption{Comparison of intensity transformations under Paillier}
	\label{tbl:it-pal}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_decrypted.png} \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

\begin{table*}
	\caption{Comparison of intensity transformations under Dasgupta--Pal}
	\label{tbl:it-dp}
	\begin{tabular}{m{1cm}*{7}{>{\centering\arraybackslash}m{1.75cm}}}
		\toprule
		\multirow{2}{*}{Image} & \multirow{2}{*}{Original} & \multicolumn{2}{c}{Image negation} & \multicolumn{2}{c}{Logarithm transformation} & \multicolumn{2}{c}{Power-law transformation} \\
							   &                           & PDT           & CDT          & PDT            & CDT           & PDT               & CDT           \\ 
		\midrule
		\xintFor #1 in {anpage, bplyce, drbost, ksunth, martin, pmives, rnpwil, sbains, swewin, yfhsie} \do {%
		\texttt{#1} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_original.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_negate_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_reference.png} & \includegraphics[width=1.75cm]{out_faces/dp_logtransform_#1_decrypted.png} & \includegraphics[width=1.75cm]{out_faces/paillier_pwrtransform_#1_reference.png} &  \\ }%
		\bottomrule         
	\end{tabular}
\end{table*}

Table~\ref{tbl:it-pal} shows the images obtained from the intensity transformation tests under the Paillier cryptosystem, while Table~\ref{tbl:it-pal} shows the resulting images from the same tests under the Dasgupta--Pal cryptosystem. Shown for each image is the original unecrypted image, and for each intensity transformation the \textit{plaintext domain transformation} (PDT) is given which is the resulting image after applying the transformation to the unencrypted image and the \textit{ciphertext domain transformation} (CDT) is the decrypted image of the processed encrypted image.

The following tables show the resulting metric scores for mean squared error (MSE), peak signal to noise ratio (PSNR), and structural similarity index (SSIM), as well as time taken (in seconds) for encrypting the input image ($t_\text{enc}$), applying an operation to the encrypted image ($t_\text{apply}$), and decrypting the resulting encrypted image ($t_\text{dec}$), for each image in the test set. Tables~\ref{tbl:neg-pal} and~\ref{tbl:neg-dp} show the results obtained from applying image negation, Tables~\ref{tbl:log-pal} and~\ref{tbl:log-dp} from applying logarithm transformation, and Tables~\ref{tbl:pwr-pal} and~\ref{tbl:pwr-dp} from applying power-law transformation.

\subsubsection{Image Negation}
Both the Paillier and Dasgupta--Pal cryptosystems were able to perform image negation under the encrypted domain without introducing noise in the resulting image. In other words, the resulting image from doing image negation on an image on the clear and doing image negation under the encrypted domain are identical, as evidenced by the mean squared errors being exactly equal to zero, the PSNR being infinite, and the SSIM being exactly equal to one.

@@

\begin{table}[h]
	\caption{Image negation under Paillier}
	\label{tbl:neg-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
        \texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.128 & 0.013 & 0.041 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.013 & 0.024 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.031 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.109 & 0.012 & 0.048 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.117 & 0.015 & 0.043 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.111 & 0.012 & 0.025 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.099 & 0.012 & 0.023 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.084 & 0.012 & 0.024 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.089 & 0.012 & 0.023 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.081 & 0.012 & 0.029 \\
		\bottomrule
    \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Image negation under Dasgupta--Pal}
	\label{tbl:neg-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.000 & $\infty$ & 1.00000 & 0.221 & 30.217 & 0.239 \\
		\texttt{bplyce} & 0.000 & $\infty$ & 1.00000 & 0.190 & 30.919 & 0.216 \\
		\texttt{drbost} & 0.000 & $\infty$ & 1.00000 & 0.284 & 31.182 & 0.268 \\
		\texttt{ksunth} & 0.000 & $\infty$ & 1.00000 & 0.225 & 32.581 & 0.223 \\
		\texttt{martin} & 0.000 & $\infty$ & 1.00000 & 0.220 & 32.220 & 0.271 \\
		\texttt{pmives} & 0.000 & $\infty$ & 1.00000 & 0.287 & 31.224 & 0.294 \\
		\texttt{rnpwil} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.478 & 0.284 \\
		\texttt{sbains} & 0.000 & $\infty$ & 1.00000 & 0.186 & 29.784 & 0.362 \\
		\texttt{swewin} & 0.000 & $\infty$ & 1.00000 & 0.243 & 38.407 & 0.220 \\
		\texttt{yfhsie} & 0.000 & $\infty$ & 1.00000 & 0.285 & 29.488 & 0.449 \\		
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Logarithm Transformation}
Unlike image negation, logarithm transformation involves more operations, so the increase in processing time for both cryptosystems are expected. Applying the logarithm transformation under Paillier took about 2 seconds per image, while it took about 13.5 minutes each under Dasgupta--Pal.

The logarithm transformation under Dasgupta--Pal turned out to be more accurate than Paillier, whose mean squared errors approach zero and the SSIM values approach one for every image as shown in Table~\ref{tbl:log-dp}. Although the results from using Paillier show that it is also accurate enough with the mean squared errors being less than 30 and the SSIM values average to 0.99, Dasgupta--Pal has been able to produce an almost identical result to that of the plaintext domain transformation counterparts. This observation is rather unexpected, considering that the implementation used for Paillier is more robust (due to its use of external C/C++ libraries which makes computations faster).

\begin{table}[h]
	\caption{Logarithm transformation under Paillier}
	\label{tbl:log-pal}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 13.369 & 36.870 & 0.99263 & 0.085 & 1.813 & 0.023 \\
		\texttt{bplyce} & 7.072 & 39.635 & 0.99017 & 0.089 & 2.073 & 0.023 \\
		\texttt{drbost} & 8.151 & 39.019 & 0.98688 & 0.091 & 1.913 & 0.023 \\
		\texttt{ksunth} & 25.253 & 34.108 & 0.98927 & 0.089 & 1.919 & 0.023 \\
		\texttt{martin} & 10.374 & 37.971 & 0.98695 & 0.106 & 1.829 & 0.023 \\
		\texttt{pmives} & 2.426 & 44.283 & 0.99401 & 0.127 & 1.900 & 0.023 \\
		\texttt{rnpwil} & 5.184 & 40.985 & 0.98971 & 0.096 & 1.853 & 0.023 \\
		\texttt{sbains} & 16.772 & 35.885 & 0.98492 & 0.081 & 1.746 & 0.024 \\
		\texttt{swewin} & 5.803 & 40.494 & 0.99241 & 0.091 & 1.827 & 0.027 \\
		\texttt{yfhsie} & 12.192 & 37.270 & 0.99354 & 0.081 & 1.815 & 0.023 \\
		\bottomrule
        \end{tabular}
\end{table}
\begin{table}[h]
	\caption{Logarithm transformation under Dasgupta--Pal}
	\label{tbl:log-dp}
    \begin{tabular}{lcccccc}
        \toprule
        Image & MSE  & PSNR & SSIM & $t_\text{enc}$ & $t_\text{apply}$ & $t_\text{dec}$ \\ \midrule
		\texttt{anpage} & 0.004 & 71.624 & 0.99999 & 0.287 & 802.957 & 0.036 \\
		\texttt{bplyce} & 0.000 & 82.043 & 1.00000 & 0.190 & 815.384 & 0.048 \\
		\texttt{drbost} & 0.004 & 72.480 & 1.00000 & 0.270 & 813.640 & 0.036 \\
		\texttt{ksunth} & 0.000 & 87.372 & 1.00000 & 0.204 & 804.629 & 0.047 \\
		\texttt{martin} & 0.001 & 77.421 & 1.00000 & 0.245 & 822.940 & 0.036 \\
		\texttt{pmives} & 0.001 & 76.934 & 1.00000 & 0.194 & 814.132 & 0.036 \\
		\texttt{rnpwil} & 0.000 & 83.135 & 1.00000 & 0.197 & 808.503 & 0.047 \\
		\texttt{sbains} & 0.001 & 77.301 & 1.00000 & 0.270 & 809.406 & 0.047 \\
		\texttt{swewin} & 0.006 & 70.004 & 0.99999 & 0.268 & 813.217 & 0.051 \\
		\texttt{yfhsie} & 0.001 & 78.576 & 1.00000 & 0.243 & 830.640 & 0.039 \\
		\bottomrule
        \end{tabular}
\end{table}

\subsubsection{Power-Law Transformation}
Unlike in the previous intensity transformations, applying the power-law transformation under both cryptosystems produced less than accurate images. The accuracy varies greatly across all the images as in the case of Paillier, with mean squared errors as high as 8270.696 and as low as 616.419, and SSIM scores ranging from 0.43185 to 0.92334. As expected, the total processing time now takes about 20 seconds per image since the power-law transformation is more computationally intensive due to its approximation of an infinite series consisting of terms using the logarithm function, which is also approximated using a combination of addition and multiplication operations.
